\section{Commit Message}
\label{sec:message}

%To help classify commits by purpose, we need to use multiple data sources, and one of the most important is the commit message.
One of the most important sources of information to help us classify commits is the commit message.
Commit messages are explanations provided by developers when they push their changes to shared developing repositories.
The messages include the rationales of those changes and help others to understand what the developers did.
Thus, the commit messages are important materials that research can use to help categorize commits. 
In fact, in the most studies we mentioned in the previous section, they use commit messages as a major resource for automating classifying commits.
Beyond this, there are works in which researchers automate generating commit messages for commits to support development.
We believe this is also an important application for this research, since a well-established categorization will provide important and well-structured information of what the commits do.

\subsection{Use Commit Messages to Classify Commits}

We will use code as our major source for categorization. 
But we will also make use of commit messages.
One of the major challenges in this step will be removing useless information.
To achieve this, we will apply natural language processing techniques at this stage.

\subsection{Automated Message Generation}

There are existing works for automatic commit message generation. For example, Cortes et al. \cite{cortes2014automatically} introduce ChangeScribe approach for automatic message generation and Linares et al. \cite{linares2015changescribe} demonstrate the approach.
Jiang et al. \cite{jiang2017automatically } automatically generating commit messages from code changes by applying neural machine translation techniques.

However, they don't have a core, well-grained categorization to support message generation.
Our categorization will provide support for it.

